Towards End-user Web Scraping For Customization

### 2021-02-14 paper.tex
Fixed typos after pasting into gdoc

\begin{figure*}
  \includegraphics[width=\textwidth]{media/creating.png}
  \caption{\label{fig:creating} Creating an adapter: 1) column data will be scraped into, 2) system's controls, 3) demonstrated column value and row from which colums should be demonstrated from 4) column values determined by generalization algorithm 5) column values populated in table, 6) next column to scrape data into and 7) button to save adapter created by demonstration}
\end{figure*}

@@

This type of divide between tasks appears in other domains. In data
science, workflows revolve between cleaning and using data but this
often happens in different environments. The creators of Wrex
\citep{drosos2020}, an end-user programming-by-example system for data
wrangling, reported that ``although data scientists were aware of and
appreciated the productivity benefits of existing data wrangling tools,
having to leave their native notebook environment to perform wrangling
limited the usefulness of these tools.'' This was a major reason Wrex
was developed as an add-on to Jupyter notebooks, the environment in
which data scientists use their data. In web scraping, if a user comes
across an omission while working with data scraped from a website, they
need to switch from the environment in which they are using the data to
the environment in which they created their scraping code in order to
edit and re-run it. This can be seen in many end-user web scraping
systems like Rousillon \citep{chasins2018}and FlashExtract
\citep{le2014} and commercial tools like import.io \citep{zotero-77},
dexi.io \citep{dexi.io}, Octoparse \citep{zotero-83} and ParseHub
\citep{zotero-86}. In web customization, the creators of Vegemite
\citep{lin2009}, a system for end-user programming of mashups, reported
that participants of its user study thought ``it was confusing to use
one technique to create the initial table, and another technique to add
information to a new column.'' This hints at the need for both a unified
environment and a unified workflow.

In this work, we have combined scraping and customization into a single,
unified environment with a unified workflow. The goal is to minimize the
environment switch between \emph{extracting} the data and \emph{using}
the data. A user might start out by scraping some data on a website, and
then switch to customizing the website using the results. Then, they
might realize they need more data to perform their desired task, at
which point they can easily extend the adapter by demonstrating new
columns. All of these tasks take place right in the browser, where the
user was initially already using the website. Instead of bringing the
data to another tool, we have brought a tool to the data. This directly
relates to the idea of ``in-place toolchains'' \citep{zotero-60} being
an integral part of end-user programming systems.

@@

Many end-user web scraping and macro systems allow users to
\emph{create} programs by demonstration but do not offer a way to
\emph{edit} them by demonstration. In Rousillon \citep{chasins2018}, a
web scraping program created by demonstration can only be edited through
a high-level, block-based programming language called Helena
\citep{zotero-51}. Helena supports adding control flow logic
(conditional execution, wait times etc) which is invaluable for
automating access to websites. However, it does not support extending
the web scraping code to add new columns after the demonstration or
repairing it to provide new selectors if the website changes. In
Vegemite \citep{lin2009}, a web automation program created through
demonstration can only be edited by editing the text-based
representation of the automtation demonstrations. In fact, only the
demonstrations used to perform automations on the scraped website data
can be edited. If a user needs to add a new column or repair an
exisiting one in the scraped data table, they need to re-demonstrate the
columns and then re-run the automation script. One exception to existing
editing models worth pointing out is import.io \citep{zotero-77}. It
allows users to add new columns by demonstration but it is not clear
whether deleting a column and re-demonstrating it could serve the
purpose of repair.

@@

Many successful end-user programming systems such as spreadsheets and
SQL provide users with immediate results after entering commands. Our
live programming environment is particularly similar to that of
FlashProg \citep{mayer2015}, a framework that provides user interface
support for programming-by-demonstration systems like FlashExtract
\citep{le2014}, and relates to the idea that an important quality of
end-user programming is ``interaction with a living system''
\citep{zotero-60}.

Unlike text-based commands which are only valid once complete (e.g
\texttt{SELECT\ *\ FRO} versus \texttt{SELECT\ *\ FROM\ user\_table}),
the target of demonstration commands (the value of a DOM element under
the cursor) is the same during both hover and click (incomplete command
verus complete command). This allows us to take a small step further by
executing a command before a user completes it, thereby providing them
with a preview of the results on hover.

@@

FlashProg \citep{mayer2015} is a framework that provides user interface
support for FlashExtract \citep{le2014}, a framework for data scraping
by examples. FlashProg's interface provides immediate visual feedback
about the generalization and scrapes the matched values into an output
tab. In addition, it has a program viewer tab that contains a high level
description of what the generated program is doing and provides a list
of alternative programs. Finally, it has a disambiguation tab that
utilizes conversational clarification to disambiguate programs, the
conservations with the user serving as inputs to generate better
programs. Though FlashProg has many desirable features we aim to
implement in future iterations, it does not offer a unified environment
within a browser for scraping and customizing websites.

Rousillon \citep{chasins2018} is a tool that enables end-users to scrape
distributed, hierarchical web data. Its interface does not provide
\emph{full} live feedback about its generalizations or the values to be
scrapped until all the demonstrations have been provided and the
generated program has been run. If run on a website it has encountered
before, Rousillon makes all the previously determined generalizations
visible to the user by color-coding the values on the website that
belong to the same column. This is a desirable feature for our system as
users will not have to actively explore in order to discover which
values are available for scraping and how they are related to each
other. On the extension and repair front, Rousillon presents the web
scraping code generated by demonstration as an editable, high-level,
block-based language called Helena \citep{zotero-51}. While Helena can
be used to perform more complex editing tasks like adding control flow,
it does not support adding or repairing columns after the demonstrations
and presents a change in the model used for creation. Our system
maintains the model used for creation by allowing users to extend and
repair web scraping code via demonstration.

@@

Sifter \citep{huynh2006} is a tool that augments well structured
websites with advanced sorting and filtering functionality. Like
Wildcard, it uses web scraping to extract data from websites in order to
enable customizations (sorting and filtering). Unlike Wildcard, it does
not support adding annotations to websites and running computations on
the scraped data using a spreadsheet formula language. Both of these
significantly expand the types of customizations end-users can make to
websites. Sifter performs the web scraping automatically using a variety
of heuristics and solicits guidance from the user if this fails. While
automatic web scraping seems desirable, it is unclear how useful it is
if the goal is customization. Given a row with ten scrapable values, and
therefore ten columns, would a user prefer to simply demonstrate the
value for the single column they are interested in or un-demonstrate the
nine values they are not interested in? This automatic web scraping
aproach can be also be seen in tools like import.io \citep{zotero-77} so
it is certainly worth evaluating as part of a user study.

@@

Like existing approaches, web scraping in our current implementation is
limited to what can be demonstrated. This is problematic if users want
to scrape the URL associated with a link element, which is not visible,
or only scrape a substring of a value. To solve this, we plan to harness
Wildcard's formula language. End-users will be able to use formulas
targeted at web scraping to access DOM element properties and
attributes. For example, a formula like
\texttt{=GetAttribute(link\_column,\ ‘href’)} could be used to scrape
URLs of link elements. End-users will also be able to use formulas
targeted at data processing. For example, a formula like
\texttt{=GetSubstring(name\_column,\ 1,\ 2)} could be used to scrape
substrings of text values. Such web scraping and data processing
formulas will give end-users some of the power available to programmers
that write web scraping code in Javascript which supports a wide variety
of DOM access and processing ability.

To assess our design principles, we plan to carry out a broader
evaluation of our system through a user study. So far, we have only
tested the system amongst overselves and a small number of collegues.
More testing is needed to understand whether it can be succussfully used
among a broader set set of users across a wider variety of websites.
Furthermore, we plan to incorporate the program viewer and
disambiguation features of FlashProg \citep{mayer2015} to give users
more insight and control into the generalization process.

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth]{media/creating.png}
  \caption{\label{fig:creating} Creating an adapter: 1) column data will be scraped into, 2) system's controls, 3) demonstrated column value and row from which columns should be demonstrated from 4) column values determined by generalization algorithm 5) column values populated in table, 6) next column to scrape data into and 7) button to save adapter created by demonstration}
\end{figure*}

@@

This type of divide between tasks appears in other domains. In data
science, workflows revolve between cleaning and using data but this
often happens in different environments. The creators of Wrex
\citep{drosos2020}, an end-user programming-by-example system for data
wrangling, reported that ``although data scientists were aware of and
appreciated the productivity benefits of existing data wrangling tools,
having to leave their native notebook environment to perform wrangling
limited the usefulness of these tools.'' This was a major reason Wrex
was developed as an add-on to Jupyter notebooks, the environment in
which data scientists use their data. In web scraping, if a user comes
across an omission while working with data scraped from a website, they
need to switch from the environment in which they are using the data to
the environment in which they created their scraping code in order to
edit and re-run it. This can be seen in many end-user web scraping
systems like Rousillon \citep{chasins2018}and FlashExtract
\citep{le2014} and commercial tools like import.io \citep{import.io},
dexi.io \citep{dexi.io}, Octoparse \citep{octoparse} and ParseHub
\citep{parsehub}. In web customization, the creators of Vegemite
\citep{lin2009}, a system for end-user programming of mashups, reported
that participants of its user study thought ``it was confusing to use
one technique to create the initial table, and another technique to add
information to a new column.'' This hints at the need for both a unified
environment and a unified workflow.

In this work, we have combined scraping and customization into a single,
unified environment with a unified workflow. The goal is to minimize the
environment switch between \emph{extracting} the data and \emph{using}
the data. A user might start out by scraping some data on a website, and
then switch to customizing the website using the results. Then, they
might realize they need more data to perform their desired task, at
which point they can easily extend the adapter by demonstrating new
columns. All of these tasks take place right in the browser, where the
user was initially already using the website. Instead of bringing the
data to another tool, we have brought a tool to the data. This directly
relates to the idea of ``in-place toolchains'' \citep{zotero-1362} being
an integral part of end-user programming systems.

@@

Many end-user web scraping and macro systems allow users to
\emph{create} programs by demonstration but do not offer a way to
\emph{edit} them by demonstration. In Rousillon \citep{chasins2018}, a
web scraping program created by demonstration can only be edited through
a high-level, block-based programming language called Helena
\citep{zotero-1349}. Helena supports adding control flow logic
(conditional execution, wait times etc) which is invaluable for
automating access to websites. However, it does not support extending
the web scraping code to add new columns after the demonstration or
repairing it to provide new selectors if the website changes. In
Vegemite \citep{lin2009}, a web automation program created through
demonstration can only be edited by editing the text-based
representation of the automation demonstrations. In fact, only the
demonstrations used to perform automations on the scraped website data
can be edited. If a user needs to add a new column or repair an existing
one in the scraped data table, they need to re-demonstrate the columns
and then re-run the automation script. One exception to existing editing
models worth pointing out is import.io \citep{import.io}. It allows
users to add new columns by demonstration but it is not clear whether
deleting a column and re-demonstrating it could serve the purpose of
repair.

@@

Many successful end-user programming systems such as spreadsheets and
SQL provide users with immediate results after entering commands. Our
live programming environment is particularly similar to that of
FlashProg \citep{mayer2015}, a framework that provides user interface
support for programming-by-demonstration systems like FlashExtract
\citep{le2014}, and relates to the idea that an important quality of
end-user programming is ``interaction with a living system''
\citep{zotero-1362}.

Unlike text-based commands which are only valid once complete (e.g
\texttt{SELECT\ *\ FRO} versus \texttt{SELECT\ *\ FROM\ user\_table}),
the target of demonstration commands (the value of a DOM element under
the cursor) is the same during both hover and click (incomplete command
versus complete command). This allows us to take a small step further by
executing a command before a user completes it, thereby providing them
with a preview of the results on hover.

@@

FlashProg \citep{mayer2015} is a framework that provides user interface
support for FlashExtract \citep{le2014}, a framework for data scraping
by examples. FlashProg's interface provides immediate visual feedback
about the generalization and scrapes the matched values into an output
tab. In addition, it has a program viewer tab that contains a high level
description of what the generated program is doing and provides a list
of alternative programs. Finally, it has a disambiguation tab that
utilizes conversational clarification to disambiguate programs, the
conservations with the user serving as inputs to generate better
programs. Though FlashProg has many desirable features we aim to
implement in future iterations, its implementation does not align with
our goal to provide a unified environment within a browser for scraping
and customizing websites.

Rousillon \citep{chasins2018} is a tool that enables end-users to scrape
distributed, hierarchical web data. Because demonstrations can span
across several websites and involve complex data access automation
tasks, its interface does not provide \emph{full} live feedback about
its generalizations or the values to be scrapped until all the
demonstrations have been provided and the generated program has been
run. If run on a website it has encountered before, Rousillon makes all
the previously determined generalizations visible to the user by
color-coding the values on the website that belong to the same column.
This is a desirable feature for our system as users will not have to
actively explore in order to discover which values are available for
scraping and how they are related to each other. On the extension and
repair front, Rousillon presents the web scraping code generated by
demonstration as an editable, high-level, block-based language called
Helena \citep{zotero-1349}. While Helena can be used to perform more
complex editing tasks like adding control flow, it does not support
adding or repairing columns after the demonstrations and presents a
change in the model used for creation. Our system maintains the model
used for creation by allowing users to extend and repair web scraping
code via demonstration.

@@

Sifter \citep{huynh2006} is a tool that augments well structured
websites with advanced sorting and filtering functionality. Like
Wildcard, it uses web scraping to extract data from websites in order to
enable customizations (sorting and filtering). Unlike Wildcard, it does
not support adding annotations to websites and running computations on
the scraped data using a spreadsheet formula language. Both of these
significantly expand the types of customizations end-users can make to
websites. Sifter performs the web scraping automatically using a variety
of heuristics and solicits guidance from the user if this fails. While
automatic web scraping seems desirable, it is unclear how useful it is
if the goal is customization. Given a row with ten scrapable values, and
therefore ten columns, would a user prefer to simply demonstrate the
value for the single column they are interested in or un-demonstrate the
nine values they are not interested in? This automatic web scraping
approach can be also be seen in tools like import.io \citep{import.io}
so it is certainly worth evaluating as part of a user study.

@@

Like existing programming-by-demonstration approaches, web scraping in
our current implementation is limited to what can be demonstrated. This
is problematic if users want to scrape the URL associated with a link
element, which is not visible, or only scrape a substring of a value. To
solve this, we plan to harness Wildcard's formula language. End-users
will be able to use formulas targeted at web scraping to access DOM
element properties and attributes. For example, a formula like
\texttt{=GetAttribute(link\_column,\ ‘href’)} could be used to scrape
URLs of link elements. End-users will also be able to use formulas
targeted at data processing. For example, a formula like
\texttt{=GetSubstring(name\_column,\ 1,\ 2)} could be used to scrape
substrings of text values. Such web scraping and data processing
formulas will give end-users some of the power available to programmers
that write web scraping code in Javascript which supports a wide variety
of DOM access and processing ability.

To assess our design principles, we plan to carry out a broader
evaluation of our system through a user study. So far, we have only
tested the system amongst ourselves and a small number of colleagues.
More testing is needed to understand whether it can be successfully used
among a broader set set of users across a wider variety of websites.
Furthermore, we plan to incorporate the program viewer and
disambiguation features of FlashProg \citep{mayer2015} to give users
more insight and control into the generalization process.
